Overcoming Hurdles to Green Living: Insights for Community Climate Action

### 2024-11-14 paper/paper.qmd
working on figures in data section

## Software and R-packages
## Methodology 
### Data Collection
### Data Cleaning
### Data Analysis
## Features
### Age
### Highest Level of Education Completed
### Extent Feel Informed
### Likelihood Taking Action
### Barriers Taking Action
### Best Mode of Delivery

>>>>

## Software and R-packages
## Methodology 
### Data Collection
### Data Cleaning
### Data Analysis
## Features
### Age
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: The chart illustrates the distribution of age for the 2018 survey in the City of Toronto, highlighting the major age categories.

# install libraries 
# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))

# Load necessary libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(stringr)
library(knitr)

# Read in the data from your CSV file
analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))

# Create a histogram to show the distribution of age
age_plot <- ggplot(data, aes(x = age_18)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    title = "Age Distribution of Survey Respondents (2018)",
    x = "Age",
    y = "Frequency"
  ) +
  theme_minimal()

# Display the plot
print(age_plot)

# calculate summary statistics 
mean_age <- mean(data$age_18, na.rm = TRUE)
median_age <- median(data$age_18, na.rm = TRUE)
min_age <- min(data$age_18, na.rm = TRUE)
max_age <- max(data$age_18, na.rm = TRUE)
# R does not have built in function thus needs to be defined
sd_age <- sd(data$age_18, na.rm = TRUE)
mode_age <- function(x) {
  unique_x <- unique(x)
  unique_x[which.max(tabulate(match(x, unique_x)))]
}
mode_value <- mode_age(data$age_18)

# Create a data frame with the summary statistics
summary_stats_age_18 <- data.frame(
  Statistic = c("Mean Age", "Median Age", "Mode Age", "Standard Deviation", "Minimum Age", "Maximum Age"),
  Value = c(mean_age, median_age, mode_value, sd_age, min_age, max_age)
)

# Use kable to generate a nice table
kable(summary_stats_age_18, 
      caption = "Summary Statistics for Age of Survey Respondents", 
      col.names = c("Statistic", "Value"),
      align = c("l", "c"))

```

### Highest Level of Education Completed
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: The chart illustrates the distribution of highest level of education acheived for the 2018 surveyin the city of Toronto, highlighting academic achievement.

# install libraries 
# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))

# Load necessary libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(stringr)
library(knitr)

# Read in the data from your CSV file
analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))

# Create a bar chart for the highest level of education
ggplot(data = analysis_data, aes(x = factor(highest_level_educ_18, 
       levels = c("High school or less",
                  "Some community college, vocational, trade school",
                  "Completed community college, vocational, trade school",
                  "Some university",
                  "Completed undergraduate degree",
                  "Post graduate/professional school", 
                  "Prefer not to answer")))) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(
    title = "Distribution of Highest Level of Education Achievement",
    x = "Level of Education",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.margin = margin(10, 10, 10, 10), # Adds margin around the plot
    plot.title = element_text(hjust = 0.5) # Centers the title
  ) + 
  # Wrap x-axis labels
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
  # Y-axis ticks every 25
  scale_y_continuous(breaks = seq(0, max(table(analysis_data$highest_level_educ_18)), by = 25))

# Adjust the size of the figure (increase height)
  ggsave("education_chart.png", width = 10, height = 6)
```

### Extent Feel Informed
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: The bar chart illustrates the distribution of the extent individuals feel informed about what causes climate change in the City of Toronto, based on the 2018 survey.

# install libraries 
# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))

# Load necessary libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(stringr)
library(knitr)

# Read in the data from your CSV file
analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))

# Create a bar chart for the extent people feel informed about climate change
ggplot(data = analysis_data, aes(x = factor(extent_consider_informed_18, 
       levels = c("Extremely informed", 
                  "Very informed", 
                  "Not very informed", 
                  "Not at all informed")))) +
  geom_bar(fill = "lightgreen", color = "black") +
  labs(
    title = "Extent People Feel Informed About Climate Change",
    x = "Level of Informedness",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5) # Center the title
  )

```

### Likelihood Taking Action
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: The bar chart illustrates the distribution of the likelihood of taking certain actions to address climate change in the City of Toronto based on the 2018 survey.

# install libraries 
# install.packages(c("tidyverse", "dplyr", "ggplot2", "here", "stringr", "knitr"))

# Load necessary libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(stringr)
library(knitr)

# Read in the data from your CSV file
analysis_data <- read_csv(here("data/02-analysis_data/analysis_data.csv"))

# Create reshaped data for plotting
action_data_long <- analysis_data %>%
  pivot_longer(cols = starts_with("likelihood_action"),
               names_to = "Action",
               values_to = "Likelihood") %>%
  mutate(Action = recode(Action,
                         likelihood_action_home_improvement_18 = "Home Improvement",
                         likelihood_action_reduce_hydro_18 = "Reduce Hydro Use",
                         likelihood_action_minimize_car_18 = "Minimize Car Use",
                         likelihood_action_vehicle_electric_18 = "Use Electric Vehicle",
                         likelihood_action_protein_alternative_18 = "Alternative Proteins",
                         likelihood_action_reduce_waste_18 = "Reduce Waste",
                         likelihood_action_green_product_18 = "Green Products",
                         likelihood_action_short_distance_18 = "Short Distance Travel",
                         likelihood_action_sort_waste_18 = "Sort Waste")) %>%
  filter(!is.na(Likelihood)) %>% # Remove rows where Likelihood is NA
  mutate(Likelihood = factor(Likelihood)) # Convert Likelihood to a factor

# Plot the distribution of likelihood of actions to address climate change
ggplot(action_data_long, aes(x = Action, fill = Likelihood)) +
  geom_bar(stat = "count", position = "dodge") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1), # Rotate x-axis labels for readability
        axis.title.y = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10)) +
  labs(
    title = "Likelihood of Taking Action to Address Climate Change in Toronto (2018)",
    x = "Actions to Address Climate Change",
    y = "Count of Responses",
    fill = "Likelihood"
  ) +
  scale_fill_manual(values = c("Already doing this or have done this" = "green",
                               "Very likely" = "blue",
                               "Somewhat likely" = "yellow",
                               "Somewhat unlikely" = "orange",
                               "Very unlikely" = "red"))
```

### Barriers Taking Action
### Best Mode of Delivery
